Viscous Transport in Eroding Porous Media

### 2019-07-31 docs/transport/erosion_transport.tex
some small changes to 20 body section

\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r1h_vort}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r0d5h_vort}
\includegraphics[width = 0.33 \textwidth]{./figs/1b_0d4r0d1h_vort}
\caption{\label{fig:NearWall_vort} }
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{20 nearly touching bodies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We consider 20 eroding bodies initially placed in $[-1,1] \times
[-1,1]$.  The background flow is the Hagen-Poiseuille flow
\begin{align}
  \UU(\xx)=U \left[
  \begin{array}{c}
    1-y^2 \\ 0
  \end{array}
  \right],
\end{align}
where the flow rate $U$ is chosen so that the pressure drop from $x=-2$
to $x=2$ is held fixed at 2.  We start by analyzing the effect of
erosion on the area fraction and the flow rate.  In
Figure~\ref{fig:Eroding20flowrate}(a), we plot the area fraction as a
function of normalized time.  Initially, 62\%  of the geometry eroded
bodies corresponding to a porosity of $0.38$.  As the bodies erode, the
area fraction decreases towards 0.  The trend of the area fraction
resembles that of our previous work~\cite{qua-moo2018} (Figure 10(a)),
but with a larger initial area fraction.  We also compute the flow rate
$U$ required to maintain a constant pressure drop across the channel in
Figure~\ref{fig:Eroding20flowrate}(b).  Again, the trend of $U$
resembles that of our previous work~\cite{qua-moo2018} (Figure 10(b)),
except that the initial flow rate is an order of magnitude smaller
because of the larger initial area fraction.  Starting around normalized
time $0.2$, Figure~\ref{fig:Eroding20flowrate}(b) is roughly linear
which indicates that the flow rate can be written as a power law.  Using
a line of best fit, the flow rate is approximately \begin{align} U
\approx \left(\frac{t}{t_f}\right)^{15/4}, \end{align}
\todo[inline]{update this with whatever S-H gets} which is the dashed
line in Figure~\ref{fig:Eroding20flowrate}(b).

\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/porosity20dense}
\todo[inline]{SH: Make the y-limits of this figure go from 0 to 0.7 ...
no need to make it go below 0}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/flow_rate20dense}
\todo[inline]{SH: In this figure, can you superimpose a line of best fit
from about normalized time 0.2 to normalize time 1.  Doing this crudely,
I got a slope of 15/4}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding20flowrate}(a) The area fraction of 20 nearly
 touching eroding bodies and the eroding speed versus time. 
(b) The incoming flow rate of $U$ in log scale versus time. 
Under fixed pressure drop condition, $U$ will be small initially,
increase when bodies are eroding, and grow exponentially 
to 1 when there is no body in the fluid. }
\end{figure}

@@

\begin{figure}[H]
\begin{center}
  \includegraphics[height=0.23\textwidth]{./figs/20b_dense1}
  \includegraphics[height=0.23\textwidth]{./figs/20b_dense101}
  \includegraphics[height=0.23\textwidth]{./figs/20b_dense201}
  \includegraphics[height=0.23\textwidth]{./figs/20b_dense301}
\caption{\label{fig:Eroding20vort} Erosion of 20 nearly touching bodies
with the fixed pressure drop condition. The color is the vorticity of
the fluid. The 4 snapshots are evenly spaced in time. We use $N_\iin =
256$ discretization points on the body, a time-step of $\Dt=10^{-4}$,
and smoothing parameters of $\eps= 15/256$ and $\sigma=10/256 $. In the
forth frame, bodies 4, 12, and 17 have vanished completely, and body 19
has almost completely eroded.}
\end{center}
\end{figure}

>>>>

\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r1h_vort}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r0d5h_vort}
\includegraphics[width = 0.33 \textwidth]{./figs/1b_0d4r0d1h_vort}
\caption{\label{fig:NearWall_vort} }
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{20 nearly touching bodies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We consider 20 eroding bodies initially placed in $[-1,1] \times
[-1,1]$.  The background flow is the Hagen-Poiseuille flow
\begin{align}
  \UU(\xx)=U \left[
  \begin{array}{c}
    1-y^2 \\ 0
  \end{array}
  \right],
\end{align}
where the flow rate $U$ is chosen so that the pressure drop from $x=-2$
to $x=2$ is held fixed at 2.  We start by analyzing the effect of
erosion on the area fraction and the flow rate.  In
Figure~\ref{fig:Eroding20flowrate}(a), we plot the area fraction as a
function of normalized time.  Initially, 62\% of the geometry is eroded
bodies corresponding to a porosity of $0.38$, and the area fraction
decreases to 0 as the bodies erode.  The trend of the area fraction
resembles that of our previous work~\cite{qua-moo2018} (Figure 10(a)),
but with a larger initial area fraction.  We also compute the flow rate
$U$ required to maintain a constant pressure drop across the channel in
Figure~\ref{fig:Eroding20flowrate}(b).  Again, the trend of $U$
resembles that of our previous work~\cite{qua-moo2018} (Figure 10(b)),
except that the initial flow rate is an order of magnitude smaller
because of the larger initial area fraction.  Starting around normalized
time $0.2$, Figure~\ref{fig:Eroding20flowrate}(b) is roughly linear
which indicates that the flow rate can be written as a power law.  Using
a line of best fit, the flow rate is approximately \begin{align} U
\approx \left(\frac{t}{t_f}\right)^{15/4}, \end{align}
\todo[inline]{update this with whatever S-H gets} which is the dashed
line in Figure~\ref{fig:Eroding20flowrate}(b).

\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/porosity20dense}
\todo[inline]{SH: Make the y-limits of this figure go from 0 to 0.7 ...
no need to make it go below 0}
\caption{}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/flow_rate20dense}
\todo[inline]{SH: In this figure, can you superimpose a line of best fit
from about normalized time 0.2 to normalize time 1.  Doing this crudely,
I got a slope of 15/4}
\caption{}
\end{subfigure}
\caption{\label{fig:Eroding20flowrate}(a): The area fraction of 20
nearly touching eroding bodies versus normalized time. (b): The incoming
flow rate, $U$, for a fixed pressure drop across the channel versus
normalized time.  The flow rate is initially very small, but it
eventually increases as a power law (dashed line) towards the flow rate
$U=1$ that occurs once all the bodies have eroded.}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
  \includegraphics[height=0.23\textwidth]{./figs/20b_dense1}
  \includegraphics[height=0.23\textwidth]{./figs/20b_dense101}
  \includegraphics[height=0.23\textwidth]{./figs/20b_dense201}
  \includegraphics[height=0.23\textwidth]{./figs/20b_dense301}
  \todo[inline]{S-H: Increase the font of the colorbar}
\caption{\label{fig:Eroding20vort} Erosion of 20 nearly touching bodies
with the fixed pressure drop condition. The color is the vorticity of
the fluid. The 4 snapshots are evenly spaced in time. We use $N_\iin =
256$ discretization points on the body, a time-step of $\Dt=10^{-4}$,
and smoothing parameters of $\eps= 15/256$ and $\sigma=10/256 $. In the
forth frame, bodies 4, 12, and 17 have vanished completely, and body 19
has almost completely eroded.}
\end{center}
\end{figure}
